Staged Abstract Interpreters

### 2019-09-08 paper/20_prelim.tex
Begone spaces
and -> or

In this section, we first describe the abstract syntax of the language for our interpreters. 
Then we present the generic interpreter shared among the four different
semantics. After which, we instantiate the interpreter to the concrete one.
It is worth noting that we choose to use Scala and monadic style to
demonstrate the idea, but the approach is not restricted to this
choice. One can use imperative or direct style in other MSP languages
(e.g., MetaOCaml \cite{DBLP:conf/gpce/CalcagnoTHL03, DBLP:conf/flops/Kiselyov14}
and Template Haskell \cite{Sheard:2002:TMH:636517.636528}) to construct
such staged abstract interpreters.

>>>>

In this section, we first describe the abstract syntax of the language for our
interpreters. Then, we present the generic interpreter shared among the four
different semantics, after which we instantiate the interpreter to the concrete
one. It is worth noting that we choose to use Scala and a monadic style to
demonstrate this idea, though the approach is not restricted to this choice.
Indeed, one can use imperative or direct style in other MSP languages (e.g.,
MetaOCaml \cite{DBLP:conf/gpce/CalcagnoTHL03, DBLP:conf/flops/Kiselyov14} or
Template Haskell \cite{Sheard:2002:TMH:636517.636528}) to construct such staged
abstract interpreters.
